```{r setup_sparse_telem, warning=FALSE, include=FALSE, echo=FALSE, message=FALSE, output=FALSE}
library(knitr)
library(tidyr)
library(purrr)
library(dplyr)
library(sf)
library(lubridate)
library(ggplot2)
library(kableExtra)

source('telemetry_tools.R')

knitr.duplicate.label = "allow"
knitr::opts_chunk$set(fig.path = "images/")
```

# Comparing Drivers' Live (Sparse) Telemetry

In this chapter, we will start to explore the extent we can compare the live telemtry data traces of different drivers. Note that te data may be quite sparse at times, which might limit what we are able to do.

Where large gaps exist between data samples, we are more likely to require a sensible time model more the stage to try to minimise errors in using a simple, linear interpolator to generate missing data.

## Load Route Data

Get the route in a UTM form:

```{r}
geojson_filename = "data/finland_2021.geojson"
geojson_sf = sf::st_read(geojson_filename)

# Use a convenience function tjat loads in the geojson file
# and then generates a spatial features dataframe with a UTM projection
stage_route_utm = get_route(geojson_sf, 7)

stage_route_utm
```
### Generate Buffered Route

We can also take this opportunity to create a buffered route for filtering the telemetry data:

```{r}
#Use a convenience function to get buffered route
buffered_route = get_buffered_route(stage_route_utm, 50, crs=original_crs, utm=FALSE)

leaflet(buffered_route) %>% 
  addProviderTiles("OpenTopoMap", group = "OSM") %>% 
  addPolylines(color = "red", weight = 2)
```

## Load Driver Data

Load in data for a handful of drivers:

```{r}
# Path to the telem data
path = "../../wrcplus/notebooks/2021_secto_Rally_Finland"
```

```{r}
evans_min_telem = get_min_telem("Evans", "SS7", path)
evans_min_telem_utm = evans_min_telem %>%
                        st_transform(crs = st_crs(utm_proj4_string))

# Get the buffer filtered data
route_telem_evans = get_route_telem(stage_route_utm,
                                    evans_min_telem,
                                    evans_min_telem_utm)
evans_min_telem_utm
```

We can always preview the data just to check that it is sensible:

```{r}
library(leaflet)

tmp_route <- evans_min_telem %>% st_coordinates() 

leaflet(tmp_route) %>% 
  addProviderTiles("OpenTopoMap", group = "OSM") %>% 
  addPolylines(color = "purple", weight = 5)

```

Let's get some data for some other drivers:

```{r}
fourmaux_min_telem = get_min_telem("Fourmaux", "SS7", path)

fourmaux_min_telem_utm = fourmaux_min_telem %>%
                            st_transform(crs = st_crs(utm_proj4_string))

route_telem_fourmaux = get_route_telem(stage_route_utm,
                                       fourmaux_min_telem,
                                       fourmaux_min_telem_utm)

fourmaux_min_telem_utm
```

```{r}
breen_min_telem = get_min_telem("Breen", "SS7", path)

breen_min_telem_utm = breen_min_telem %>%
                            st_transform(crs = st_crs(utm_proj4_string))

route_telem_breen = get_route_telem(stage_route_utm,
                                       breen_min_telem,
                                       breen_min_telem_utm)

route_telem_breen
```

And preview the telemetry sample points for all the drivers we have gathered telemetry data for:

```{r}
leaflet( )  %>% 
  addProviderTiles("OpenTopoMap", group = "OSM") %>% 
  addCircleMarkers(data=route_telem_evans, radius=1, color="blue") %>%
  addCircleMarkers(data=route_telem_breen, radius=1,color="red") %>%
  addCircleMarkers(data=route_telem_fourmaux, radius=1, color="black")
```

## Get Annotated Route Telemetry

The route telemetry annotation includes the distance along the stage route for each telemetry sample:

```{r}
route_telem_evans_utm = to_utm(route_telem_evans)
route_telem_evans_utm = route_telem_evans_utm %>% 
                          get_telem_dists(stage_route_utm)
#route_telem_evans_utm


route_telem_fourmaux_utm = to_utm(route_telem_fourmaux)
route_telem_fourmaux_utm = route_telem_fourmaux_utm %>% 
                          get_telem_dists(stage_route_utm)
route_telem_fourmaux_utm
```

## Create Driver Estimators

From the annotated data can generate some naive estimators for stage time along route based on distance along route:

```{r}

fourmaux_time_estimator = approxfun(c(0, route_telem_fourmaux_utm$dist),
                           c(0, route_telem_fourmaux_utm$newdelta_s))

evans_time_estimator = approxfun(c(0, route_telem_evans_utm$dist),
                           c(0, route_telem_evans_utm$newdelta_s))

```


Let's see if a visual comparison reveals anything:

```{r}
# Sample every 500m
vals = seq(to=max(c(route_telem_fourmaux_utm$dist,
                    route_telem_evans_utm$dist)), by=500)

ggplot() + 
  # Predicted line in pink
  geom_line(aes(x=vals, y=evans_time_estimator(vals)), size=1, colour='blue') +
  geom_point(data=route_telem_evans_utm,
             aes(x=dist, y=newdelta_s), size=1, colour='red') +
  # Sampled times in black
  geom_line(aes(x=vals, y=fourmaux_time_estimator(vals)),
            color='red', size=1) +
  geom_point(data=route_telem_fourmaux_utm,
             aes(x=dist, y=newdelta_s), size=1, colour='blue')

```

