
Now we need to find the nearest point on the actual route for each line to get a fair distance into route measure; use the UTM projection so we get things in meters:

```{r}
full_pois = st_sfc(st_multipoint(st_coordinates(telem_df_full_utm)),
                      crs=st_crs(telem_df_full_utm))

# Generate a list of points from a multipoint
# Via: https://github.com/r-spatial/sf/issues/114
full_pois_points = st_cast(x = full_pois, to = "POINT")
```


```{r}
# how many points in route?
test_route  %>% st_coordinates() %>% length()
```

```{r}
#how many data samples?
length(full_pois_points)
```

```{r}
library(sfnetworks)

route_dg = as_sfnetwork(st_geometry(route_telem_utm), directed = TRUE)

blended = st_network_blend(route_dg, full_pois_points)
```

```{r}
plot(route_dg, cex=0.5, col = 'grey', lwd = 6)

plot(blended, cex=0.5, col='red', add=TRUE)

plot(full_pois_points, col='blue', cex=0.1, add=TRUE)
```


```{r}
blended
```

Generate a line of points along the route that the telemetry points are closest too.

Note that there may be end effects is the start location of route and actual stage (from telemetry) don't match).



It looks like the supplied route data is not brilliant...

```{r}
head(dist, 30)
```

Find distance along line of nearest point on line - - need to convert this to UTM (meters).


```{r}
point = as(route_telem,'Spatial')
  
zz = as.data.frame(rgeos::gProject(as(test_route, "Spatial"), point))
```


```{r}
as(test_route, "Spatial")
                
```

We are perhaps safer using `trajr` to find the distance along the route as generate from the pure telemetry:

```{r}

utm_telem_full = st_transform(telem_df_full,
                              crs=utm_proj4_string) %>% 
  mutate(lat = st_coordinates(.)[,1],
                lon = st_coordinates(.)[,2])

trj <- TrajFromCoords(utm_telem_full %>% select(lon, lat, utc),
                      xCol="lon", yCol="lat", timeCol="utc")

trj$distance = Mod(trj$displacement)

trj$cum_dist = cumsum(trj$distance)

trj$speed  = telem_df_full$speed
trj$brk  = telem_df_full$brk
trj$throttle  = telem_df_full$throttle
trj$rpm  = telem_df_full$rpm
trj$t  = telem_df_full$t
trj
```
```{r}
ggplot(trj) +geom_line(aes(y=t,x=cum_dist)) 
```

Could also try estimating the distance based on speed and time etc.



```{r}
ggplot(trj) +geom_line(aes(x=cum_dist,y=speed)) +
    geom_line(aes(x=cum_dist,y=throttle), color='green') + geom_line(aes(x=cum_dist,y=brk), color='red')  
```



*We might still be able to hack something from the route using the live data (low quality), perhaps by starting some distance into the stage...*


# BELOW junk???


test_near2  = test_near %>% st_coordinates() %>% st_zm()
#test_near2['speed'] = route_telem['speed']

leaflet(test_near2 ) %>% 
  addCircleMarkers() %>%
  addProviderTiles("OpenTopoMap", group = "OSM")
```



 st_intersection(buffered_route, l2)



trj <- TrajFromCoords(telem_df_min_ %>% select(lon, lat, utc),
                      xCol="lon", yCol="lat", timeCol="utc")

trj$distance = Mod(trj$displacement)

trj$cum_dist = cumsum(trj$distance)

trj

plot(trj)

ggplot(trj)+geom_line(aes(x=displacementTime, y=cum_dist))

```